---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The {RMT3DMS} R package<br><small><font color="#999">Pre- and post-processing of MT3DMS & MT3D-USGS files</font></small>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/RMT3DMS.svg)](https://CRAN.R-project.org/package=RMT3DMS)
<!-- badges: end -->

The {[RMT3DMS](https://rogiersbart.github.io/RMT3DMS)} R package provides a set of tools for solute transport modelling
with [MT3DMS](https://hydro.geo.ua.edu/mt3d/mt3dms2.htm) &
[MT3D-USGS](https://water.usgs.gov/ogw/mt3d-usgs/). It is closely related to the
{[RMODFLOW](https://rogiersbart.github.io/RMODFLOW/)} package for groundwater
flow modelling. The functionality is targeted at feature-parity with that of the
[ModelMuse](https://www.usgs.gov/software/modelmuse-a-graphical-user-interface-groundwater-models)
GUI and friends, albeit restricted to the
[MODFLOW-2005](https://www.usgs.gov/software/modflow-2005-usgs-three-dimensional-finite-difference-ground-water-model)
family of codes.

## Install

You can install the latest version of
{[RMT3DMS](https://rogiersbart.github.io/RMT3DMS)} with any of the following:

```{r eval = FALSE}
renv::install("rogiersbart/RMT3DMS")
pak::pkg_install("rogiersbart/RMT3DMS")
remotes::install_github("rogiersbart/RMT3DMS")
```

If you don't have {[renv](https://rstudio.github.io/renv/)},
{[pak](https://pak.r-lib.org/)}, or {[remotes](https://remotes.r-lib.org/)}
installed, try this instead:

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("rogiersbart/RMT3DMS")
```

## Use

Similar to {[RMODFLOW](https://rogiersbart.github.io/RMODFLOW)}, the
{[RMT3DMS](https://rogiersbart.github.io/RMT3DMS)} package provides a set of
functions to work on a file-by-file basis, and another to work with complete
models. If you have an existing MT3D model, a good place to start is trying to
read it in completely with:

```{r eval = FALSE}
library(RMT3DMS)
my_model <- rmt_read("my-model.mt_nam")
```

And looking at the resulting object's structure:

```{r eval = FALSE}
str(my_model)
```

You can install the solute transport codes in the default location with:

```{r eval = FALSE}
rmt_install()
```

And check if this went fine:

```{r eval = FALSE}
rmt_installed_codes()
```

To run your model, try:

```{r eval = FALSE}
rmt_execute("my-model.mt_nam")
```

## Note

A more extensive introduction to the package will be available soon.
